Manuscript Te example

### 2019-11-12 ManuscriptTe.Rmd
Update examples

#Microclimate calculations
u_z=function(z, d=0.229, z_0=0.0208, u_star= 0.114, k=0.41) u_star/k*log((z-d)/z_0)

```{r}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
dat=read.csv("microclimate_C1.csv", sep=",", na.strings = c("-49.99","NA"))
```
```{r}
#ANALYZE SURFACE ROUGHNESS AND PROFILES
C1all$day=  as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$mday
C1all$hour=as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$hour

@@

C1.hr= as.matrix(C1.hr)
#surface roughness
z0= apply(C1.hr[, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], FUN=surface_roughness, MARGIN=1, zr=c(0.25,0.5,1.5,1.5))

z.seq <- seq(0, 2, by = 0.1)

for(hr in 1:24){
t.seq1 <- air_temp_profile_neutral(T_r=C1.hr[hr,"Air0.5m"], zr=0.5, z0=0.02, z=2, T_s=C1.hr[hr,"Soil"])
t.seq2 <- air_temp_profile(T_r=C1.hr[hr,"Air0.5m"], u_r=C1.hr[hr,"Wind0.5m"], zr=0.5, z0=0.02, z=2, T_s=C1.hr[hr,"Soil"])
t.seq3 <- air_temp_profile_segment(T_r=C1.hr[hr, c("Air0.25m","Air0.5m","Air1.0m","Air1.5m")],u_r=C1.hr[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.25,0.5,1,1.5), z0=0.02, z=2, T_s=C1.hr[hr,"Soil"])

u.seq1<- wind_speed_profile_neutral(u_r=C1.hr[hr,"Wind0.5m"], zr=0.5, z0=0.02, z=2)
u.seq2<- wind_speed_profile(u_r=C1.hr[hr,"Wind0.5m"], zr=0.5, z0=0.02, z=2)
u.seq3<- wind_speed_profile_segment(u_r=C1.hr[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.25,0.5,1,1.5), z0=0.02, z=2)
}

#plot(t.seq, z.seq, type = "l", xlab = "Temperature (C)", ylab = "z (height above ground in m)")
```

>>>>

#Microclimate calculations
```{r}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
dat=read.csv("microclimate_C1.csv", sep=",", na.strings = c("-49.99","NA"))
```
```{r}
#ANALYZE SURFACE ROUGHNESS AND PROFILES
C1all$day=  as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$mday
C1all$hour=as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$hour

@@

C1.hr= as.matrix(C1.hr)
```

We can estimate surface roughness across hours:
```{r}
#surface roughness
z0= apply(C1.hr[, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], FUN=surface_roughness, MARGIN=1, zr=c(0.25,0.5,1.0,1.5))

We calculate the temperature and windspeed profiles for a given hour using multiple functions in TrenchR.
```{r}
z.seq <- seq(0, 2, by = 0.1)

#subset to day and hour
C1.sub= subset(C1.dayhr, C1.dayhr$day==10)
hr=10

#estimate profiles
#temperature
t.seq1= sapply(z.seq, FUN=air_temp_profile_neutral, T_r=C1.sub[hr,"Air0.5m"], z0=z0[hr], zr=0.5, T_s=C1.sub[hr,"Soil"])

t.seq2= sapply(z.seq, FUN=air_temp_profile, T_r=C1.sub[hr,"Air0.5m"], u_r=C1.hr[hr,"Wind0.5m"], zr=0.5, z0=z0[hr], T_s=C1.sub[hr,"Soil"])

t.seq3= sapply(z.seq, FUN=air_temp_profile_segment, T_r=C1.sub[hr, c("Air0.25m","Air0.5m","Air1.0m","Air1.5m")],u_r=C1.sub[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.25,0.5,1,1.5), z0=rep(z0[hr],4), T_s=C1.sub[hr,"Soil"])

#windspeed
u.seq1= sapply(z.seq, FUN=wind_speed_profile_neutral, u_r=C1.sub[hr,"Wind0.5m"], zr=0.5, z0=z0[hr])

u.seq2= sapply(z.seq, FUN=wind_speed_profile, u_r=C1.sub[hr,"Wind0.5m"], zr=0.5, z0=z0[hr])

u.seq3= sapply(z.seq, FUN=wind_speed_profile_segment, u_r=C1.sub[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.25,0.5,1,1.5), z0=rep(z0[hr],4))

#replace infinity with N
t.seq1[which(!is.finite(t.seq1))]=NA
```

We then plot the temperature and windspeed profiles.
```{r}
plot(t.seq1, z.seq, type = "l", xlab = "Temperature (C)", ylab = "z (height above ground in m)")
points(t.seq2, z.seq, type = "l", lty="dashed")
points(t.seq3, z.seq, type = "l", lty="dotted")
points(C1.sub[hr, c("Air0.25m","Air0.5m","Air1.0m","Air1.5m")], c(0.25,0.5,1,1.5), type = "l", col="red")

plot(u.seq1, z.seq, type = "l", xlab = "windspeed (m/s)", ylab = "z (height above ground in m)")
points(u.seq2, z.seq, type = "l", lty="dashed")
points(u.seq3, z.seq, type = "l", lty="dotted")
points(C1.sub[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], c(0.25,0.5,1,1.5), type = "l", col="red")
```
